\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
added key words 'renormalization group equations' as per Jae-hyeon suggestion.
removed reference to FlexibleSUSY bugs in section 8 as per Jae-hyeon suggestion.

\begin{keyword}
sparticle, 
supersymmetry, 
Higgs
\PACS 12.60.Jv
\PACS 14.80.Ly
\end{keyword}
\end{frontmatter}

@@

For checking the correctness of \fs's generated spectrum generators
extensive unit tests against Softsusy's MSSM and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
were done: We checked mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles and found all to agree within double machine
precision.  We also compared the overall pole mass spectrum after the
full fixed-point iteration has finished, and found the spectra to
agree at the sub-permille level.  Analytic tests of the $R$-symmetric
low-energy model, MRSSM, were done by Philip Diessner and several bugs
in \fs and SARAH were identified and fixed.

\fs generated NUH \ESSM has also been compared against a handwritten
spectrum generator for a constrained version of the \ESSM
\cite{Athron:2009bs,Athron:2012pw}.  The RGEs could be compared
directly in unit tests and were found to match.  The handwritten code
doesn't include full one loop self energies or tadpoles so tests on
these were not carried.  Although the generators assume different
constraints they could be compared by using the output of the
CE$_6$SSM as input to \fs and the spectra were found to be in
reasonable agreement, given the different levels of precision.

>>>>

\begin{keyword}
sparticle, 
supersymmetry, 
Higgs,
renormalization group equations
\PACS 12.60.Jv
\PACS 14.80.Ly
\end{keyword}
\end{frontmatter}

@@

For checking the correctness of \fs's generated spectrum generators
extensive unit tests against Softsusy's MSSM and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
were done: We checked mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles and found all to agree within double machine
precision.  We also compared the overall pole mass spectrum after the
full fixed-point iteration has finished, and found the spectra to
agree at the sub-permille level.  Analytic tests of the $R$-symmetric
low-energy model, MRSSM, were done by Philip Diessner and several bugs
in SARAH were identified and fixed.

\fs generated NUH \ESSM has also been compared against a handwritten
spectrum generator for a constrained version of the \ESSM
\cite{Athron:2009bs,Athron:2012pw}.  The RGEs could be compared
directly in unit tests and were found to match.  The handwritten code
doesn't include full one loop self energies or tadpoles so tests on
these were not carried.  Although the generators assume different
constraints they could be compared by using the output of the
CE$_6$SSM generator as an input to \fs and the spectra were found to be in
reasonable agreement, given the different levels of precision.
